Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-16 research_class/paper.tex
Remove redundant list of functionality groups?
I think it's clear enough without the repitition.

The last three functionality groups focus on interactive audio and video
applications and are less relevant to Raft over WebRTC. The WebRTC
section of the bibliography %TODO: reference link
has a (partial) list of WebRTC specific protocol drafts and other
related protocol standards for the first three functionality groups
(data transport, data framing and security, and connection
management).

>>>>

The last three functionality groups focus on interactive audio and video
applications and are less relevant to Raft over WebRTC. The WebRTC
section of the bibliography %TODO: reference link
has a (partial) list of WebRTC specific protocol drafts and other
related protocol standards for the first three functionality groups.
